### 2016-06-11 sec6_optimization.tex
Checkpoint
Saved algo part

\section{Optimizing SPM}
\label{sec:optimization}
It is notable that Algorithm~\ref{algo:apriori_mining} takes exponential
time to mine GCMP. There are two major factors dragging 
down the performance. First, the size of $Sr_s$ affects the initial 
size of $2$-patterns. Second, the candidates generated in each 
level affects the join performance.
In this section, we describe several practical techniques to boost the performance
of SPM.
%We have analyzed that the bottlenecks of Algorithm~\ref{algo:apriori_mining} 
%lies in two factors. The size of each $Sr_s$ and the size of candidates in each level of Apriori.
%In this section, we provide several optimizations to boost the bottlenecks.
%\subsection{Edge Reduction by Direction}
%The first spot for reducing the size of $Sr_s$ is to remove the replicated edges. As shown in Algorithm~\ref{algo:spm_overview}, each edge in the conceptual graph is replicated twice in generating the star-structure. The purpose of replication is to ensure the completeness of star partition. However, this replication can be avoided if we choose an appropriate way of partitioning. 
%
%We design the edge partitioning method by edge direction. Instead of building a conceptual graph that is undirected, we create the directed conceptual graph as follows: First, we assign each object a unique number. Then
%for a cluster $C_t$ in snapshot $S_t$, for any pair $(u,v) \in C_t$, an edge $e(u,v) = \{t\}$ is created if $u < v$. It is easy to see that the directed conceptual graph is a DAG. We then create each $Sr_u$ by including all the outgoing edges of $u$. By so doing, each edge is assigned to only one star, thus avoids the replications. We use the following theorem to ensure the completeness of the edge direction method.
%
%\begin{theorem}[Sound and Completeness of Edge Direction]
%Star partition with edge direction is sound and complete.
%\end{theorem}
%\begin{proof}
%It is notable that each star is a subset of original trajectories, thus the soundness is trivially true. For completeness, if $P$ is valid pattern, then let $s$ be the object of the smallest number in $P.O$, i.e., $s=\min_{o \in P.O}(o)$. Since $s$ is smallest and the all other objects in $P.O$ is connected with $s$. Therefore, $P.O \equiv Sr_s$, which indicates that $P.O$ is also a pattern in $Sr_s$.
%\end{proof}
%An example of edge direction is shown in Figure~\ref{fig:star_partition}. As shown,
%by adapting the direction method, half the size of $S_r$'s is reduced. This clearly brings efficiency in both shuffling and apriori mining.

\subsection{Edge Simplification}
Each edge $e(s,v)$ in $Sr_s$ contains a time sequence $ET$ 
which represents the co-occurrence of $s$ and $v$. We notice that the edge 
between $s$ and $t$ is not always necessary. For example, if an edge has a
cardinality less than $K$, it is unnecessary to include this edge to 
$Sr_s$ since it cannot contribute to any patterns.
This motivates us to simplify the edges in $Sr_s$ 
to boost the overall performance.

Our goal of edge simplification is to, given a time sequence $T$, find a subsequence
of $T' \subseteq T$, such that $T'$ is potentially conforms to $K,L,G$. And we
wish $|T'|$ to be as small as possible.  
We star-off by observing that for every time sequence $T$, $T$ can be 
divided into a set of maximally $G$-connected subsequences. Note that
a maximally $G$-connected subsequence can potentially contribute to
a pattern if it conforms to $K,L$.
Therefore, we are able to reduce $T$
to its maximally $G$-connected subseuqnces which conform to $K,L$.

To formally describe the idea, we define the \emph{candidate sequence} as follows:

@@

\begin{definition}[Candidate Sequence]
Given the pattern parameters: $L,K,G$, a sequence $T$ is a \emph{Candidate Sequence} 
if for any of its maximal $G$-connected sequence $T'$, $T'$ conforms to $L,K$.
\end{definition}

For example, let $L = 2, K = 4, G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11,13)$ is 
not a fully candidate sequence since one of its maximal $G$-connected sequence $(9,10,11)$
is not a partly candidate sequence. In contrast, sequence $T_2=(1,2,4,5,6)$ is 
a fully candidate sequence.

To reduce a sequence $T$ to a candidate sequence, we need to strip out its 
maximal $G$-connected subsequences which does not form to $K,L$. Such a reduction
takes two rounds scan of $T$ as shown in Algorithm~\ref{algo:simp_prune}. In the 
first round, the consecutive portions of $T$ with size less than $L$ are removed.
In the second round, the maximal $G$-connected sequences of size less than $K$ are
removed. Clearly the simplification algorithm runs in linear time.
\begin{algorithm}
\caption{Edge Simplification}
\label{algo:simp_prune}
\begin{algorithmic}[1]
\Require $T$
\State{---Remove the consecutive segment with size less than $L$---}
\State $c \gets 0$
\For {$i \in (0,...,|T|)$}
	\If{$T[i] - T[i-1] != 1$} 
		\If{$i - c < L$} 
			\State $T$ remove $[c:i)$
		\EndIf
		\State $c \gets i$
	\EndIf
\EndFor
\State{---Remove the $G$-connected segment with size less than $K$---}
\State $s\gets 1$, $c\gets 0$
\For{$i \in (0: |T|)$}
	\If{$T[i] - T[i-1] > G$}
		\If{$s < K$}   
			\State $T$ remove $[c:i)$
		\EndIf
		\State {$c \gets i$, $s \gets 1$}
	\Else
		\State $s++$
	\EndIf
\EndFor
\end{algorithmic}
\end{algorithm}

\begin{example}
Take $T_1=\{1,2,4,5,6,9,10,11,13\}$ as an example of edge simplification. Let $L = 2, K = 4, G = 2$.
In the first round of scan. $T_1$ reduces to $\{1,2,4,5,6,9,10,11\}$. The consecutive subsequence $\{13\}$
is removed by $L=2$. $T_1$ has two maximal $G$-consecutive subsequences, which 
are $\{1,2,4,5,6\}$ and $\{9,10,11\}$. Since $K=4$, $\{9,10,11\}$ is removed
from $T_1$ in the second round of scan. Therefore, $T_1$ is simplified to $\{1,2,4,5,6\}$.
\end{example}

@@

By leveraging the edge simplification technique, 
the size of the edges in $Sr_s$ can be greatly reduced. If
an edge cannot be reduced to a candidate sequence, then it is directly removed from $Sr_s$.
If an edge can be reduced to a candidate sequence, replacing itself 
by the candidate sequence results in a more compact storage.

@@

\subsection{Temporal monotonicity}
During the apriori phase, we repeatedly join candidate patterns in different levels to generate a larger set
of a patterns. We observe that traditional monotonic property of Apriori algorithms \textbf{does not}
hold in GCMP mining. That is given two candidate $P_1, P_2$, if $P_1.O \subset P_2.O$ and $P_1$ is not 
a valid pattern, then $P_2$ may or may not be a valid pattern. However, we notice that
we may form another monotonic property based on the \emph{candidate sequence} such that
the Apriori algorithm could still benefit.

The intuition is that if a candidate $P_1.T$ cannot be reduce to a \emph{candidate sequence}, then $P_1$ cannot 
be valid pattern. Furthermore, any candidate $P_2$, with $P_1.O \subset P_2.O$ cannot be a valid pattern.
This \emph{temporal monotonic property} 
is explicitly described as in the follow theorem:

\begin{theorem}[Temporal Monotonic Property of GCMP]
Given the temporal parameters $L,G,K$, for a candidate $c$ in Algorithm~\ref{algo:apriori_mining},
if $c.T$ cannot be reduced to a candidate sequence, then for any candidate $c'$ with $c.O \subset c'.O$, $c'$ can be pruned.
\end{theorem}
\begin{proof}
Let $c_1$, $c_2$ be two candidates with $c_1.O \subset c_2.O$. It is easy to see that $c_1.T \supseteq c_2.T$.
If $c_1.T$ cannot be reduced to a candidate sequence, then any subset of $c_1.T$ cannot
be reduced. It follows that $c_2.T$ cannot be reduced neither. Thus,
if $c_1.T$ cannot be reduced to a candidate sequence, $c_2$ can be pruned. 
\end{proof}

\subsection{Forward closure checking}
Although leveraging \emph{temporal monotonicity} could largely prune false candidates and reduce
the apriori search space, it is ineffective when a \textit{true} pattern exists. 
For example, if a final pattern of a star $Sr_s$ is the \textit{union of all vertices} in the star, 
then in apriori, ${|Sr_s|}\choose{i + 1}$ candidates needs to be generated at 
each level $i$. This results in an exponential search space while
the output only contains one pattern.  
In general, when candidates at level $i$ collectively forms a true pattern, 
running aprior produces many wasted candidates.

Let $Lv_i$ be the set of candidates at level $i$ of Algorithm~\ref{algo:apriori_mining},
we use the \emph{forward closure} $FC_i$ to denote the union of the objects in
all candidates in $Lv_i$. Then, the \emph{forward closure checking} is stated as follows:
\begin{theorem}[Forward Closure Checking Rule]
Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
and directly output $FC_i$.
\end{theorem}

\begin{proof}
We prove by contradiction. Suppose there exists another pattern $P$ such that $P.O \neq FC_i$, let 
$X=P.O - FC_i \neq \emptyset$. Consider a subset of $P$ which contains $X$ with size $i+1$, (i.e., $P_1 \subseteq P, P_1\subseteq X, |P_1|=i+1$). Since $P$ is a proper pattern, then $P_1$ is also a proper pattern. Therefore $P_1 \in Lv_i$.
Then it follows $X$ is in the forward closure of $FC_i$, (i.e.,$X \in FC_i$), which contradicts with $X\notin FC_i$.
\end{proof}

It is notable that, as the level grows in Algorithm~\ref{algo:apriori_mining}, the closure $FC$
reduces, thus the pruning power of $FC$ would be stronger.

%To facilitate efficient mining, we adapt the \emph{forward closure checking} rule to 
%quickly determine whether it is sufficient to terminate the apriori search. Given the candidates at
%level $i$ $Lv_i$, we define the \emph{forward closure} of $Lv_i$ as the union of objects from
%all candidates. Then, the following \emph{forward closure checking} rule can be used:
%
%\begin{theorem}[Forward Closure Checking Rule]
%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining}, the forward closure
%is $\mathbb{F}_i = \cup_{cand \in Lv_i} (cand.O) $. Algorithm~\ref{algo:apriori_mining} terminates when 
%$FC_i$ forms a valid GCMP .
%\end{theorem}

@@

Induced by the Theorem 5, taking object IDs as the numbering (i.e., in Algorithm~\ref{algo:spm_overview})
would be guaranteed to produce a partition which is almost optimal.
%By definition, $c_i = \Sigma_{1\leq j \leq n} a_{i,j}$, is a sum of $n$ independent 0-1 variables.
%Taking expectation on both sides, we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} a_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$. Let $\mu =E[c_i] = d/2$, $\delta = \sqrt{12\log n/d}$, by Chernoff Bound, 
%the following holds:
%\begin{equation*}
%\begin{split}
%	Pr(c_i \geq (1+ \delta)\mu) & \leq \exp(-\mu \delta^2 / 3) \\
%						&= \exp(-d/2 \times 12 \log n / 3d ) \\
%						&= \exp(-2\log n) = n^{-2}
%\end{split}
%\end{equation*}
%
%Next, since the event $\max_{1\leq j \leq n}(c_j) > (1+ \delta)\mu$ can be viewed as
%$\cup_{c_i} (c_i > (1+ \delta)\mu )$, by Union Bound, we achieve the following:
%\begin{equation*}
%\begin{split}
%	Pr(||A\vec{b}||_\infty > (1+ \delta)\mu)) &=Pr(\max_{1\leq j \leq n}(c_j) > (1+ \delta)\mu)  \\
%		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq (1+ \delta)\mu) \\
%		& = n^{-1} = 1/n
%\end{split}
%\end{equation*}
%Substitute $\mu$ and $\delta$, we achieve the following concise form:
%\begin{equation*}
%	Pr(||A\vec{b}||_\infty > (d/2 + \sqrt{3 d\log n})) \leq 1/n
%\end{equation*}
%This indicates that, the probability of $(||A\vec{b}||_\infty-d/2)$ being less than $ O(\sqrt{d\log n})$ is $(1-1/n)$. Notice that $||A^*\vec{b}||_\infty \geq d/2$, therefore, with probability greater than $(1-1/n)$, the difference between $||A\vec{b}||_\infty$ and $||A^*\vec{b}||_\infty$ is less than $O(\sqrt{d\log n})$.
%\end{proof} 
%
%Theorem 5 is powerful enough to induce the following lemma:
%\begin{theorem}[Load Balance of Algorithm~\ref{algo:spm_overview}]
%The partitioning in Algorithm~\ref{algo:spm_overview} differs at most $O(\sqrt{d\log |\mathbb{O}|})$ 
%from optimal partitioning with probability $(1-1/|\mathbb{O}|)$.
%\end{theorem}

>>>>

\section{Optimizing SPM}
\label{sec:opt}
In Algorithm~\ref{algo:apriori_mining}, there are
 two major factors affecting the performance.
First, the edges in $Sr_s$ affects the initial 
size of $2$-patterns. Second, the candidates generated in each 
level affects the join performance.
In this section, we describe several practical 
techniques to boost the performance.
%We have analyzed that the bottlenecks of Algorithm~\ref{algo:apriori_mining} 
%lies in two factors. The size of each $Sr_s$ and the size of candidates in each level of Apriori.
%In this section, we provide several optimizations to boost the bottlenecks.
%\subsection{Edge Reduction by Direction}
%The first spot for reducing the size of $Sr_s$ is to remove the replicated edges. As shown in Algorithm~\ref{algo:spm_overview}, each edge in the conceptual graph is replicated twice in generating the star-structure. The purpose of replication is to ensure the completeness of star partition. However, this replication can be avoided if we choose an appropriate way of partitioning. 
%
%We design the edge partitioning method by edge direction. Instead of building a conceptual graph that is undirected, we create the directed conceptual graph as follows: First, we assign each object a unique number. Then
%for a cluster $C_t$ in snapshot $S_t$, for any pair $(u,v) \in C_t$, an edge $e(u,v) = \{t\}$ is created if $u < v$. It is easy to see that the directed conceptual graph is a DAG. We then create each $Sr_u$ by including all the outgoing edges of $u$. By so doing, each edge is assigned to only one star, thus avoids the replications. We use the following theorem to ensure the completeness of the edge direction method.
%
%\begin{theorem}[Sound and Completeness of Edge Direction]
%Star partition with edge direction is sound and complete.
%\end{theorem}
%\begin{proof}
%It is notable that each star is a subset of original trajectories, thus the soundness is trivially true. For completeness, if $P$ is valid pattern, then let $s$ be the object of the smallest number in $P.O$, i.e., $s=\min_{o \in P.O}(o)$. Since $s$ is smallest and the all other objects in $P.O$ is connected with $s$. Therefore, $P.O \equiv Sr_s$, which indicates that $P.O$ is also a pattern in $Sr_s$.
%\end{proof}
%An example of edge direction is shown in Figure~\ref{fig:star_partition}. As shown,
%by adapting the direction method, half the size of $S_r$'s is reduced. This clearly brings efficiency in both shuffling and apriori mining.

\subsection{Edge Simplification}
Each edge $e(s,v)$ in $Sr_s$ contains a time sequence $ET$ 
which represents the co-occurrence of $s$ and $v$. We notice that the edge 
between $s$ and $v$ is not always necessary. For example, if an edge has a
cardinality less than $K$, it is unnecessary to include this edge to 
$Sr_s$ since it cannot contribute to any patterns.
This motivates us to simplify the edges in $Sr_s$.

Our intuition is thus to, remove the unnecessary timestamps among 
the edges in a star, such that the valid patterns
would not be affected. To realize this idea,
we formally design the concept of \emph{candidate sequence} as follows:

\begin{definition}[Candidate Sequence]
Given the pattern parameters: $L,K,G$, a sequence $T$ is a \emph{Candidate Sequence} 
if for any of its maximal $G$-connected sequence $T'$, $T'$ conforms to $L,K$. 
\end{definition}
For example, let $L = 2, K = 4, G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11,13)$ is 
not a candidate sequence since one of its maximal $2$-connected sequence $(9,10,11,13)$
does not conform to $L$. In contrast, sequence $T_2=(1,2,4,5,6,8,9)$ is 
a candidate sequence.

Not that, although $T_1$ is not a candidate sequence, it can be simplified
to a candidate sequence (i.e, $T_2$). Generally, for any time sequence $T$, 
if it does not contain a \emph{candidate sequence}, then it cannot contribute
to any valid patterns. In fact, only the candidate sequence inside $T$ affects
the final patterns. Therefore, we may use the candidate sequence to simplify edges in 
a star. During the simplification, if an edge results in a candidate
sequence of size zero, then it is removed from the star. Otherwise,
the simplified edge is kept. By so doing, the size of the new star
is much smaller.

We design an efficient linear time algorithm for the simplification process.
It takes two rounds scan of $T$ as shown in Algorithm~\ref{algo:simp_prune}. 
In the first round, the consecutive portions of $T$ with size less than $L$ are removed.
In the second round, the maximal $G$-connected sequences of size less than $K$ are
removed. Clearly the simplification algorithm takes $O(T)$ time.

%Our goal of edge simplification is to, given a time sequence $T$, find a 
%subsequence of $T' \subseteq T$, such that $T'$ conforms to $K,L,G$. And we
%wish $|T'|$ to be as small as possible.  
%We star-off by observing that for every time sequence $T$, $T$ can be 
%divided into a set of maximally $G$-connected subsequences. Note that
%a maximally $G$-connected subsequence can potentially contribute to
%a pattern if it conforms to $K,L$.
%Therefore, we are able to reduce $T$
%to its maximally $G$-connected subseuqnces which conform to $K,L$.

%To formally describe the idea, we define the \emph{candidate sequence} as follows:

@@

%\begin{definition}[Candidate Sequence]
%Given the pattern parameters: $L,K,G$, a sequence $T$ is a \emph{Candidate Sequence} 
%if for any of its maximal $G$-connected sequence $T'$, $T'$ conforms to $L,K$.
%\end{definition}
%
%For example, let $L = 2, K = 4, G = 2$, sequence $T_1=(1,2,4,5,6,9,10,11,13)$ is 
%not a fully candidate sequence since one of its maximal $G$-connected sequence $(9,10,11)$
%is not a partly candidate sequence. In contrast, sequence $T_2=(1,2,4,5,6)$ is 
%a fully candidate sequence.

\begin{algorithm}
\caption{Edge Simplification}
\label{algo:simp_prune}
\begin{algorithmic}[1]
\Require $T$
\State{---$L$ Phase---}
\State $c \gets 0$
\For {$i \in (0,...,|T|)$}
	\If{$T[i] - T[i-1] > 1$} 
		\If{$i - c < L$} 
			\State $T$ remove $[c:i)$
		\EndIf
		\State $c \gets i$
	\EndIf
\EndFor
\State{---$G$-$K$ Phase---}
\State $s\gets 1$, $c\gets 0$
\For{$i \in (0: |T|)$}
	\If{$T[i] - T[i-1] > G$}
		\If{$s < K$}   
			\State $T$ remove $[c:i)$
		\EndIf
		\State {$c \gets i$, $s \gets 1$}
	\Else
		\State $s++$
	\EndIf
\EndFor
\end{algorithmic}
\end{algorithm}

\begin{example}
Take $T_1=\{1,2,4,5,6,9,10,11,13\}$ as an example of edge simplification. Let $L = 2, K = 4, G = 2$.
In the first round of scan. $T_1$ reduces to $\{1,2,4,5,6,9,10,11\}$. The consecutive subsequence $\{13\}$
is removed by $L=2$. $T_1$ has two maximal $2$-consecutive subsequences, which 
are $\{1,2,4,5,6\}$ and $\{9,10,11\}$. Since $K=4$, $\{9,10,11\}$ is removed
from $T_1$ in the second round of scan. Therefore, $T_1$ is simplified to $\{1,2,4,5,6\}$, which is shortened $44\%$.
\end{example}

@@

%
%By leveraging the edge simplification technique, 
%the size of the edges in $Sr_s$ can be greatly reduced. If
%an edge cannot be reduced to a candidate sequence, then it is directly removed from $Sr_s$.
%If an edge can be reduced to a candidate sequence, replacing itself 
%by the candidate sequence results in a more compact storage.

@@

\subsection{Temporal Monotonicity}
In Apriori, we repeatedly join candidate patterns with different sizes.
We observe that traditional monotonic property of Apriori algorithms \textbf{does not}
hold in GCMP mining. Specifically, given two candidates $P_1, P_2$, 
if $P_1.O \subset P_2.O$ and $P_1$ is not a valid pattern, 
then $P_2$ may or may not be a valid pattern. However, we notice that
we may form another monotonic property based on the \emph{candidate sequence}.

The intuition is that if a candidate $P_1.T$ cannot be simplified to 
a \emph{candidate sequence}, then $P_1$ cannot be valid pattern. 
Furthermore, any candidate $P_2$, with $P_1.O \subset P_2.O$ cannot be a valid pattern.
This \emph{temporal monotonic property} is explicitly described as in the follow theorem:

\begin{theorem}[Temporal Monotonicity]
Given the temporal parameters $L,G,K$, for a candidate pattern $P$,
if $P.T$ cannot be simplified to a candidate sequence,
then, for any candidate $P'$ with $P.O \subseteq P'.O$, $P'$ cannot be a true pattern.
\end{theorem}
\begin{proof}
Let $P_1$, $P_2$ be two candidates with $P_1.O \subseteq P_2.O$. It is easy to see that $P_1.T \supseteq P_2.T$.
Suppose $P_1.T$ cannot be simplified to a candidate sequence. Then
by proof of contradiction, any subset of $P_1.T$ cannot
be simplified. It follows that $P_2.T$ cannot be simplified to a candidate sequence. 
In summary, if $P_1.T$ cannot be simplified, $P_2$ can be pruned. 
\end{proof}

\subsection{Forward closure checking}
Although leveraging \emph{temporal monotonicity} could largely prune
false candidates and reduce the apriori search space, 
it is ineffective when a \textit{true} pattern exists. 
In an extreme case, if a final pattern of a star $Sr_s$ is 
the \textit{union of all vertices} in the star,
then in apriori, ${|Sr_s|}\choose{i + 1}$ candidates needs to be generated at 
each level $i$. This results in an exponential search space while
the output only contains one pattern.  
Generally, when candidates at level $i$ collectively forms a true pattern, 
running aprior produces many wasted candidates.

Let $Lv_i$ be the set of candidates at level $i$ of Algorithm~\ref{algo:apriori_mining},
we use the \emph{forward closure} $FC_i$ to denote the union of the objects in
all candidates in $Lv_i$. Then, the \emph{forward closure checking} is stated as follows:
\begin{theorem}[Forward Closure Checking]
Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
and directly output $FC_i$.
\end{theorem}

\begin{proof}
We prove by contradiction. Suppose there exists another pattern $P$ such that $P.O \neq FC_i$, 
let $X=P.O - FC_i \neq \emptyset$. Consider a subset $P_1$ of $P$ which contains $X$ with size $i+1$, 
(i.e., $P_1 \subseteq P, P_1\subseteq X, |P_1|=i+1$). Since $P$ is a proper pattern, 
then $P_1$ is also a proper pattern. Therefore $P_1 \in Lv_i$.
It follows $X$ is in the forward closure of $FC_i$, (i.e.,$X \in FC_i$), which contradicts with $X\notin FC_i$.
\end{proof}

It is notable that, as the level grows in Algorithm~\ref{algo:apriori_mining}, the closure $FC$
reduces, thus the pruning power of $FC$ would be stronger. We give hybrid example of the three
optimization as follows:
%To facilitate efficient mining, we adapt the \emph{forward closure checking} rule to 
%quickly determine whether it is sufficient to terminate the apriori search. Given the candidates at
%level $i$ $Lv_i$, we define the \emph{forward closure} of $Lv_i$ as the union of objects from
%all candidates. Then, the following \emph{forward closure checking} rule can be used:
%
%\begin{theorem}[Forward Closure Checking Rule]
%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining}, the forward closure
%is $\mathbb{F}_i = \cup_{cand \in Lv_i} (cand.O) $. Algorithm~\ref{algo:apriori_mining} terminates when 
%$FC_i$ forms a valid GCMP .
%\end{theorem}

@@

%By definition, $c_i = \Sigma_{1\leq j \leq n} a_{i,j}$, is a sum of $n$ independent 0-1 variables.
%Taking expectation on both sides, we get: $E[c_i] = E[\Sigma_{1\leq j \leq n} a_{i,j}]=E[\Sigma_{1\leq j \leq n} e_{i,j}]/2 = d/2$. Let $\mu =E[c_i] = d/2$, $\delta = \sqrt{12\log n/d}$, by Chernoff Bound, 
%the following holds:
%\begin{equation*}
%\begin{split}
%	Pr(c_i \geq (1+ \delta)\mu) & \leq \exp(-\mu \delta^2 / 3) \\
%						&= \exp(-d/2 \times 12 \log n / 3d ) \\
%						&= \exp(-2\log n) = n^{-2}
%\end{split}
%\end{equation*}
%
%Next, since the event $\max_{1\leq j \leq n}(c_j) > (1+ \delta)\mu$ can be viewed as
%$\cup_{c_i} (c_i > (1+ \delta)\mu )$, by Union Bound, we achieve the following:
%\begin{equation*}
%\begin{split}
%	Pr(||A\vec{b}||_\infty > (1+ \delta)\mu)) &=Pr(\max_{1\leq j \leq n}(c_j) > (1+ \delta)\mu)  \\
%		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq (1+ \delta)\mu) \\
%		& = n^{-1} = 1/n
%\end{split}
%\end{equation*}
%Substitute $\mu$ and $\delta$, we achieve the following concise form:
%\begin{equation*}
%	Pr(||A\vec{b}||_\infty > (d/2 + \sqrt{3 d\log n})) \leq 1/n
%\end{equation*}
%This indicates that, the probability of $(||A\vec{b}||_\infty-d/2)$ being less than $ O(\sqrt{d\log n})$ is $(1-1/n)$. Notice that $||A^*\vec{b}||_\infty \geq d/2$, therefore, with probability greater than $(1-1/n)$, the difference between $||A\vec{b}||_\infty$ and $||A^*\vec{b}||_\infty$ is less than $O(\sqrt{d\log n})$.
%\end{proof} 
%
%Theorem 5 is powerful enough to induce the following lemma:
%\begin{theorem}[Load Balance of Algorithm~\ref{algo:spm_overview}]
%The partitioning in Algorithm~\ref{algo:spm_overview} differs at most $O(\sqrt{d\log |\mathbb{O}|})$ 
%from optimal partitioning with probability $(1-1/|\mathbb{O}|)$.
%\end{theorem}
